---
title: "Apriori"
author: "Namrata Walanj"
date: "May 12, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r lib}
library(readr)
library(dplyr)
library(tidyr)
library(arules)
library(arulesViz)
library(methods)
```

## Loading datasets prior products and products
```{r order_products}
ordr_pr <- read_csv("order_products__prior.csv")
prods <- read_csv("products.csv")
```

## Join between prior products and products dataset by product ID to create a common data for analysis
```{r order_baskets}
order_baskets <- ordr_pr %>% 
  inner_join(prods, by="product_id") %>% 
  group_by(order_id) %>%
  summarise(basket = as.vector(list(product_name)))
```

## Converting the dataset into transactions for performing association mining.
```{r transactions}
transactions <- as(order_baskets$basket, "transactions")
```

## Product Count
```{r cnt}
itemFrequencyPlot(transactions,topN=20,type="absolute")
```



## Performing association mining
```{r associationMining}
support<-0.01
itemsets <- apriori(transactions, parameter = list(target = "frequent itemsets", supp=support, minlen=2), control = list(verbose = FALSE))
```

## Plot of most frequent itemsets
```{r plot}
basketSizes<-size(transactions)
sets_order_supp <- DATAFRAME(sort(itemsets, by="support", decreasing = F))
barplot(sets_order_supp$support, names.arg=sets_order_supp$items, xlim=c(0,0.02), horiz = T, las = 2, cex.names = .8, main = "Frequent Itemsets")
mtext(paste("support:",support), padj = .8)
product_baskets <- transactions[basketSizes > 1]
```

## Generating rules
```{r rules}
rules <- apriori(product_baskets, parameter = list(supp =  0.003269976, conf = 0.01, maxlen=3), control = list(verbose = FALSE)) 
```

## Sorted by lift value
```{r sort_rules}
inspect(sort(rules, by="lift")[1:5])
```

## Rules as per confidence to find rules which are most significant
```{r top_rules}
top_rules = inspect(sort(rules, by="confidence")[1:10])
```

## Before purchasing banana the most significant rules ordered by confidence are
```{r alt_rules}
rules2<-apriori(data=product_baskets, parameter=list(supp=0.0032,conf = 0.01), 
               appearance = list(default="lhs",rhs="Banana"),
               control = list(verbose=F))

rules2<-sort(rules2, decreasing=TRUE,by="confidence")
inspect(rules2[1:15])
```

## After purchasing Banana the most significant rules depicted by confidence are
```{r apriori}
rules3<-apriori(data=product_baskets, parameter=list(supp=0.0032,conf = 0.01), 
               appearance = list(default="rhs",lhs="Banana"),
               control = list(verbose=F))
rules3<-sort(rules3, decreasing=TRUE,by="confidence")
inspect(rules3[1:15])
```
